A Bioconductor Workflow for Processing and Analysing Spatial Proteomics Data

### 2016-09-06 bioc-workflow.Rmd
add todo re plot3D and marker clustering
remove peason cor, as this is nonsense anyway

@@

## Peason correlation

```{r pearson}
i1 <- exprs(hl[, hl$Replicate == 1])
i2 <- exprs(hl[, hl$Replicate == 2])
pearcor <- cor(t(i1), t(i2))
pearcor0 <- cor(t(i1[, seq(1, 10, 2)]), t(i2[, seq(1, 10, 2)]))
mean(diag(pearcor))
mean(diag(pearcor0))
```

- What about classification on different replicates?

>>>>

**TODO** Possibly mention `plot3D` and `mrkHClust`, although these are
only available in the development version.

@@
